Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
minor changes

\todo{Explain the algorithm with pseudocode?}
Local variables: committed, a map from commands to dependency sets, initially the empty map.
\begin{itemize}[noitemsep,nolistsep]
    \item Upon ${propose\left( c \right)}^p$: call ${announce\left( c \right)}^p$.
    \item Upon ${suggest\left( c,d \right)}^p$: call ${propose\left( c,d \right)}^p$.
    \item Upon ${decide\left( c,d \right)}^p$: insert the mapping $c \rightarrow d$ in the map ``committed''.
    \item Periodically: process the committed commands, as described below.
\end{itemize}

The variable ``committed'' of the algorithm above can be seen as describing a directed graph $g$ whose vertices are commands and such that there is an edge from $c_1$ to $c_2$ if and only if ``committed'' maps $v_1$ to a set $deps$ where $v_2\in deps$, i.e. $v_1$ depends on $v_2$.

>>>>

\todo{Explain the algorithm with pseudocode?}

Local variables: $\operatorname{committed}_p$, a map from commands to dependency sets, initially the empty map.
\begin{itemize}[noitemsep,nolistsep]
    \item Upon ${\operatorname{propose}\left( c \right)}^p$: call ${\operatorname{announce}\left( c \right)}^p$.
    \item Upon ${\operatorname{suggest}\left( c,d \right)}^p$: call ${\operatorname{propose}\left( c,d \right)}^p$.
    \item Upon ${\operatorname{decide}\left( c,d \right)}^p$: insert the mapping $c \rightarrow d$ in the map $\operatorname{committed}_p$.
    \item Periodically,  every process $p$ processes $\operatorname{committed}_p$, as described below.
\end{itemize}

The local variable $committed_p$ of a process $p$ can be seen as describing a directed graph $g_p$ whose set of vertices $V\left( g_p \right)$ is the domain of $\operatorname{commited}_p$ and such that there is an edge from $c_1$ to $c_2$ if and only both are in $V\left( g_p \right)$ and $v_2 \in \operatorname{commited}_p\left[ v_1 \right]$ (i.e., $v_1$ depends on $v_2$).
%Let us assume that
